---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FishPlot

<!-- badges: start -->
<!-- badges: end -->

The goal of FishPlot is to plot the fish caught on the DFO Maritimes Ecosystem Survey

Currently supported Species include:
  23 Redfish,
  11 Haddock,
  10 Cod,
  14 Silver hake,
  16 Pollock,
  30 Halibut,
  220 Dogfish,
  40 Plaice,
  42 Yellowtail,
  200 Barndoor skate
  

## Installation

You can install the development version of FishPlot from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BradHubley/FishPlot")

#or

devtools::install_github("BradHubley/FishPlot")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(FishPlot)

## basic example code

RED_data.24<-subset(rv_data,YEAR==2024&SPEC==23 )
fishPlot(RED_data.24, Species="Redfish",lab=2024,ladj=0.001,jadj=0.2,nadj=0.01,lscale=30 )


```


